Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-24 manuscript/manuscript.Rmd
lock in data files for now
started new results

# Methods and Results

>>>>

# Results

\textbf{Training a DRL agent.}
We trained a DRL agent parametrized by a neural network $\theta$ with two hidden, 64-neuron, layers.
The state space used was a cube $[0,2]^{\times 3}$, while the policies explored mapped states $N_t$ to a single number, $h_t = \pi_\theta(N_t)$, the harvest quota on species $X$ at that timestep.
Each episode in the training and in the evaluation stages was at most 600 time steps long.
Episodes were ended early in case of a ‘‘near-extinction event,’’ a moment in which any of the populations dipped below a threshold value, i.e.,
\begin{align}
  \label{eq:thresh}
  X_t \leq X_{\text{thresh.}},\quad
  Y_t \leq Y_{\text{thresh.}},\quad
  \text{or,}\quad
  Z \leq Z_{\text{thresh.}}.
\end{align}
The reward function had two componenets:
First, at each time step the harvest $h_t$ was received as a reward.
Second, if the episode ended early (say, at time-step $t$) because of a near-extinction event, a negative reward of $-50/t$ was awarded.
The constant 50 was chosen so as to select against highly extractive policies in the early stages of training, and thus guide the agent towards sustainable policies.

We used the Ray framework [@ray_package] for training, in particular we used a Ray PPOConfig object to build the algorithm using the default values for all hyper-parameters (cf. [@repo] for the code used).
The agent was trained for 250 iterations of the PPO optimization step.

\textbf{Tuning the constant mortality strategy.}
A grid of 200 mortality rates was laid in the interval $[0, 0.1]$.
For each one of these rates, say $F$, we simulated 50 episodes based on \eqref{eq:3d model stoch}:
At each time step the state $(X_t, Y_t, Z_t)$ was observed, a harvest of $FX_t$ was collected and then the system evolved according to its natural dynamics \eqref{eq:3d model stoch}.
The optimal mortality rate was the value $F^*$ for which the mean episode reward was maximal.

\textbf{Parameter values used.}

# Old Methods and Results
